---
title: "Homework 04"
author: "Adam Guerra"
date: 05/17/2023
format: pdf
editor: visual
---

## Problem 1

```{r, include = FALSE}
#load pakcages
library(here)
library(tidyverse)
library(car)
library(sqldf)
library(janitor)
library(ggthemes)
library(naniar)

#load in data
fish_raw_data <- read_csv(here('data/NTLakes_Fish_Data.csv'))
```

#### 1. Null and Alternative Hypothesis

Mathematical

-   $H_0: \beta_1 = 0$

-   $H_A: \beta_1 \neq 0$

Biological

-   $H_0:$ Fish length is not a significant predictor of fish weight for trout perch.

-   $H_A:$ Fish length is a significant predictor of fish weight for trout perch.

#### 2. Visualize the missing data

```{r}
#clean and select data
fish_data <- sqldf("SELECT year4, spname, length, weight 
                    FROM fish_raw_data
                    WHERE spname = 'TROUTPERCH'")

#visualize missing data
vis_miss(fish_data)
             
```

As shown in the figure above, 41% of the weight category has NAs. This is going to limit how many observations I have to use in the linear model, reducing its statistical power.

#### 3. Run test

```{r}
#create linear model
fish_lm <- lm(weight ~ length, data = fish_data)

#get residuals 
fish_res <- fish_lm$residuals
```

#### 4. Visually check assumptions

###### [Repo Link](https://github.com/AdamGuerra/ENVS-193DS_homework-04_Guerra-Adam)
