---
title: "Homework 04"
author: "Adam Guerra"
date: 05/17/2023
format: pdf
editor: visual
---

## Problem 1

```{r, include = FALSE}
#load pakcages
library(here)
library(tidyverse)
library(car)
library(sqldf)
library(janitor)
library(ggthemes)
library(naniar)
library(performance)
library(flextable)
library(broom)

#load in data
fish_raw_data <- read_csv(here('data/NTLakes_Fish_Data.csv'))
```

#### 1. Null and Alternative Hypothesis

Mathematical

-   $H_0: \beta_1 = 0$

-   $H_A: \beta_1 \neq 0$

Biological

-   $H_0:$ Fish length is not a significant predictor of fish weight for trout perch.

-   $H_A:$ Fish length is a significant predictor of fish weight for trout perch.

#### 2. Visualize the missing data

```{r}
#clean and select data
fish_data <- sqldf("SELECT year4, spname, length, weight 
                    FROM fish_raw_data
                    WHERE spname = 'TROUTPERCH'")

#visualize missing data
vis_miss(fish_data)
             
```

As shown in the figure above, 41% of the weight category has NAs. This is going to limit how many observations I have to use in the linear model, reducing its statistical power.

#### 3. Run test

```{r}
#create linear model
fish_lm <- lm(weight ~ length, data = fish_data)

#get residuals 
fish_res <- fish_lm$residuals
```

#### 4. Visually check assumptions

```{r, fig.width = 8, fig.height = 6}
#diagnostic plots
par(mfrow = c(2,2))
plot(fish_lm)

```

#### 5. Descriptions of diagnostic plots

-   Residuals vs Fitted: Shows residuals and fitted line to visualize constant variance. Dots appear to be evenly and randomly distributed around the line.

-   QQ: Shows both data sets against one another. Data appears to be normally distributed.

-   Scale Location: Similar to residuals vs fitted, showing homoscedasticity of variance. Data appears to be evenly and randomly distributed around the line.

-   Residuals vs Leverage: Shows which data points are influential in the model. There are a few outliers identified that could be influential.

#### 6. Display summary of model object

```{r}
#sumary of model object
summary(fish_lm)
```

#### 7. Create summary ANOVA table

```{r}
#store ANOVA table as object
fish_squares <- anova(fish_lm)

fish_squares

#create table
fish_squares_table <- tidy(fish_squares) |> 
                      #round the sum of squares and mean squares columns to have 5 digits
                      mutate(across(sumsq:meansq, ~ round(.x, digits = 5))) |>  
                      #round the F-statistic to have 1 digit
                      mutate(statistic = round(statistic, digits = 1)) |>  
                      #replace the very very very small p value with < 0.001
                      mutate(p.value = case_when(
                             p.value < 0.001 ~ "< 0.001")) |>  
                      #rename the stem_length cell to be meaningful
                      mutate(term = case_when( term == "length" ~ "Fish Length (mm)",
                             TRUE ~ term)) |> 
                     # format(scientific = T) |> 
                      #make the data frame a flextable object
                      flextable() |> 
                      #change the header labels to be meaningful
                      set_header_labels(df = "Degrees of Freedom", 
                                        sumsq = "Sum of squares",
                                        meansq = "Mean squares",
                                        statistic = "F-statistic",
                                        p.value = "p-value") 

fish_squares_table
```

#### 8. Describe how the ANOVA table relates to the information given from summary object.

The information from this table is the relevant information about where the p-value and $R^2$ come from.

#### 9. Summarize results with in-text references to test results.

After checking the assumptions for a linear model (step 4), I performed the linear regression model of length and weight of trout that showed that length is a significant predictor of weight in trout (part 6). It also showed that 81.6% the variance in weight of trout can be explained by length. This is a high percentage, meaning that this model is a good fit.

#### 10. Visualize the model predictions and confidence intervals.

###### [Repo Link](https://github.com/AdamGuerra/ENVS-193DS_homework-04_Guerra-Adam)
